Comparing software variability across and within fMRI analysis packages

### 2022-01-03 paper/paper.tex
fix typo?

We evaluated BT for thresholded as well as unthresholded
group-level and subject-level t-statistics maps by computing the absolute
differences of t-statistic maps across tools. For WT, we computed the
average absolute difference across the three Fuzzy Libmath samples.
Moreover, we computed WT variability for a pair of tools as the sum of WT values for each tool.

>>>>

We evaluated BT for thresholded as well as unthresholded
group-level and subject-level t-statistic maps by computing the absolute
differences of t-statistic maps across tools. For WT, we computed the
average absolute difference across the three Fuzzy Libmath samples.
Moreover, we computed WT variability for a pair of tools as the sum of WT values for each tool.
